---
name: Shuo Yang(jack)
phone: +1 3474992944
aboutme: https://jack-kfk2t.ondigitalocean.app/
email: "jtwist108@gmail.com"
github: jackengtwistio
address: New York
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```
# Website Develop Skills

 * React.js
 * Node.js
 * Python
 * MongoDB
 
# Some stuff about me

 * easygoing,thoughtful,humble,cooperative,hardworking are some of the characteristics I've been always teaching myself.
 * can easily be a workaholic with a job I like
 * I want to live in NYC with stable income and meaningful job.
 * healthy diet,excercise,meditation are some of the most important things for me. 

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "bachelor(Business Administration)", "2022", "Wuhan University", "Wuhan, China"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Working Experience

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2018, "office assistant", "Run errands between offices, Organize data using office toolset",
  2019, "team member", "Recommend bicycle to tourists, Prepare and take back bicycle"
) %>% 
  brief_entries(
    glue::glue("worked as {Type}"),
    Year, 
    Desc
  )
```





